### 2021-01-29 research project/sections/Analysis_of_results.tex
""
workedo n rp. added graphs and tables

\section{Analysis of the results}

@@

\subsection{Analysis of the data}

>>>>

\section{Analysis of the results}
\newcolumntype{C}{>{\Centering\arraybackslash\hspace{0pt}}X}

@@

\subsubsection{Tabular presentation}

The arithmetic mean of the 100 trials was caluclated and the data points 
in the table shown below were found (rounded to 3 s.f.):
\begin{table}[h]
    \noindent% <-- important
    \setlength\tabcolsep{3pt} % default: 6pt
    \begin{tabularx}{\textwidth}{@{} l *{6}{C} @{}}
    \toprule
    Decimal place & Average time for approximation using Viete's method, in milliseconds (ms) & Average time for approximation using Madhava's method method, in milliseconds (ms) \\ 
    \midrule
    5  & 0.760  & 0.592   \\
    10 & 1.29  & 1.31    \\
    15 & 2.05  & 1.9     \\
    20 & 2.64  & 2.68    \\
    25 & 3.09  & 3.21    \\
    30 & 3.82  & 3.9     \\
    35 & 4.44  & 4.55    \\
    40 & 5.08  & 5.26    \\
    45 & 5.71  & 5.84    \\
    50 & 6.37  & 6.58    \\
    55 & 7.02  & 7.27    \\
    60 & 7.72  & 8.00   
    \end{tabularx}
\end{table}

\pgfplotstableread{
    X Y
    5 0.7601666451
    10 1.288158894
    15 2.050116062 
    20 2.63982296 
    25 3.091802597
    30 3.819538355 
    35 4.442822933
    40 5.081979036 
    45 5.706284046 
    50 6.370962858 
    55 7.020516396 
    60 7.723451853   
}\vietetable

\pgfplotstableread{
    X Y
    5 0.5919837952 
    10 1.307063103  
    15 1.902475357  
    20 2.679748535  
    25 3.212277889  
    30 3.904948235  
    35 4.547913074  
    40 5.255579948  
    45 5.837199688  
    50 6.578524113  
    55 7.270073891  
    60 8.004565239

}\madhavatable

\subsubsection{Graphical presentation}

To better show the trend in the data collected, the data 
has been presented in a chart below.

\begin{tikzpicture}[scale=1.2]
    \begin{axis}[
        title={Comparing the time taken for approximating the value of $\pi$},
        xlabel={Decimal places},
        ylabel={Time taken [ms]},
        xmin=0, xmax=60,
        ymin=0, ymax=10,
        ytick={0,2,4,6,8,10},
        xtick={0,20,40,60},
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
    ]

    \addplot[
        only marks,
        color=blue,
        mark=*,
        ] table {\vietetable};
        \legend{Viète's method}

    \addplot [thin, blue] table[
        y={create col/linear regression={y=Y}}
    ] % compute a linear regression from the input table
    {\vietetable};
    \addlegendentry{best fit}

    \addplot[
        only marks,
        color=red,
        mark=*,
        ] table {\madhavatable};
        \legend{Madhava's method}

    \addplot [thin, red] table[
        y={create col/linear regression={y=Y}}
    ] % compute a linear regression from the input table
    {\madhavatable};
    \addlegendentry{best fit}

    \end{axis}
\end{tikzpicture}

\subsection{Analysis}

### 2021-01-29 research project/sections/Computational_approach.tex
rp work
workedo n rp. added graphs and tables

The program made assigns the time before the execution of the method to a variable \verb|t1| 
with the \verb|time.time()| Python function. At each iteration of the method, the number of valid decimal 
places of the resultant approximation are counted and once a specified threshold is reached, 
a new \verb|t2| time variable is assigned and the time taken, defined by the difference between 
\verb|t2| and \verb|t1|, is stored. This process is repeated for all specified decimal accuracies and 
for both methods.

The \verb|mpmath| library was used for the floating point operations required 
for comparaison between approximated values and the constant $\pi$ that wouldn't 
have been possible using standard Python libraries \cite{mpmath}. The n

>>>>

The program made assigns the time before the execution of the method to a variable \verb|t1| 
with the \verb|time.time()| Python function. At each iteration of the method, the number of valid decimal 
places of the resultant approximation are counted and once a specified threshold is reached, 
a new \verb|t2| time variable is assigned and the time taken, defined by the difference between 
\verb|t2| and \verb|t1|, is stored. This process is repeated for all specified decimal accuracies and 
for both methods. The times recorded were stored in a \verb|.csv| file for further analysis.

The \verb|mpmath| library was used for the floating point operations required 
for comparison between approximated values and the constant $\pi$ that wouldn't 
have been possible using standard Python libraries \cite{mpmath}.
